Solving an Exam Scheduling Problem Using a Genetic Algorithm

### 2009-12-01 Paper/paper.tex
Updated graph on paper

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage[table]{xcolor}
\usepackage{graphicx}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PDFMARK for TeX and GhostScript
% Uncomment and complete the following for metadata if
% your paper is typeset using TeX and GhostScript (e.g
% if you use .ps or .eps files in your paper):
% \special{! /pdfmark where
% {pop} {userdict /pdfmark /cleartomark load put} ifelse
% [ /Author (John Doe, Jane Doe)
% /Title (Paper Title)
% /Keywords (AAAI, artificial intelligence)
% /DOCINFO pdfmark}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PDFINFO for PDFTeX
% Uncomment and complete the following for metadata if
% your paper is typeset using PDFTeX
\pdfinfo{
  /Title (Solving an Exam Scheduling Problem Using a Genetic Algorithm)
  /Subject (Input The Proceedings Title Here)
  /Author (Dave, Kordalewski;
           Caigu, Liu;
           Kevin, Salvesen;)
} 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Uncomment only if you need to use section numbers
% and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

      \definecolor{light-gray}{gray}{0.87}
      \rowcolors{1}{light-gray}{white}
      \begin{center}
      \begin{small}
      \begin{tabular}{*{7}{c}}
      \hline 
      	& S 	& M 	& L 	& $S_{Cor}$ & $M_{Cor}$ & $L_{Cor}$ \\ 
      \hline \hline
       d 		& 7 	& 10	& 7 	& 7 	& 10 	& 7 	\\ 
       t 		& 5		& 8 	& 8 	& 5 	& 8 	& 8 	\\ 
       $|C|$	& 20 	& 200 	& 603 	& 20 	& 200 	& 600 	\\ 
       $|R|$	& 4 	& 10 	& 43 	& 4 	& 10 	& 43	\\ 
       $|S|$	& 50 	& 300 	& 21945 & 50 	& 300 	& 21945	\\ 
       $|L_s|$	& 1-5 	& 1-6 	& 1-5 	& 2-6 	& 2-6 	& 2-6 	\\ 
       \begin{tiny}$\#$Maj\end{tiny}	& N/A 	& N/A 	& N/A 	& 4 	& 10 	& 20 	\\ 
       \begin{tiny}\textsc{sss}\end{tiny}	& $10^{182}$ & $10^{1840}$ & $10^{6695}$ & $10^{182}$ & $10^{1840}$ & $10^{6689}$ \\
      \hline 
	  \end{tabular} 
	  \end{small}
	  \end{center}

@@

    \subsubsection{Selecting Parameters for the GA}
      [\ldots]

  \subsection{Comparison Between the Different Searches}
    [\ldots]
    \begin{figure}[h!]
  	  \centering
  	  \setlength\fboxsep{0pt}
	  \setlength\fboxrule{0.5pt}
	  \fbox{\includegraphics[width=8.35cm]{SMALL_FullAverageStats}}
      \caption{Search statistics on Small data set}
	\end{figure}

>>>>

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PDFMARK for TeX and GhostScript
% Uncomment and complete the following for metadata if
% your paper is typeset using TeX and GhostScript (e.g
% if you use .ps or .eps files in your paper):
% \special{! /pdfmark where
% {pop} {userdict /pdfmark /cleartomark load put} ifelse
% [ /Author (John Doe, Jane Doe)
% /Title (Paper Title)
% /Keywords (AAAI, artificial intelligence)
% /DOCINFO pdfmark}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PDFINFO for PDFTeX
% Uncomment and complete the following for metadata if
% your paper is typeset using PDFTeX
\pdfinfo{
  /Title (Solving an Exam Scheduling Problem Using a Genetic Algorithm)
  /Subject (Input The Proceedings Title Here)
  /Author (Dave, Kordalewski;
           Caigu, Liu;
           Kevin, Salvesen;)
} 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Uncomment only if you need to use section numbers
% and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

      \definecolor{light-gray}{gray}{0.87}
      \rowcolors{1}{light-gray}{white}
      \begin{center}
      \begin{small}
      \begin{tabular}{*{7}{c}}
      \hline 
      	& S 	& M 	& L 	& $S_{Cor}$ & $M_{Cor}$ & $L_{Cor}$ \\ 
      \hline \hline
       d 		& 7 	& 10	& 7 	& 7 	& 10 	& 7 	\\ 
       t 		& 5		& 8 	& 8 	& 5 	& 8 	& 8 	\\ 
       $|C|$	& 20 	& 200 	& 603 	& 20 	& 200 	& 600 	\\ 
       $|R|$	& 4 	& 10 	& 43 	& 4 	& 10 	& 43	\\ 
       $|S|$	& 50 	& 300 	& 21945 & 50 	& 300 	& 21945	\\ 
       $|L_s|$	& 1-5 	& 1-6 	& 1-5 	& 2-6 	& 2-6 	& 2-6 	\\ 
       \begin{tiny}$\#$Maj\end{tiny}	& N/A 	& N/A 	& N/A 	& 4 	& 10 	& 20 	\\ 
       \textsc{sss}	& $10^{182}$ & $10^{1840}$ & $10^{6695}$ & $10^{182}$ & $10^{1840}$ & $10^{6689}$ \\
      \hline 
	  \end{tabular} 
	  \end{small}
	  \end{center}

@@

    \subsubsection{Selecting Parameters for the GA}
      In order to select parameters for the genetic algorithm (that is, the population, 
      number of generations to simulate, proportions of copies, randoms, mutations, and 
      crossovers for the next generation) we performed tests using the small uncorrelated 
      problem instance.

      \paragraph{Generation Parameters}
        We undertook a search of the space of parameters for forming new generations.

        In the graph below, each data point represents the average of 5 trials. To make 
        the scale clearer, the colour on the surface corresponds to the fitness, where 
        the highest fitnesses are red. The number of copies is fixed at 1, and the number 
        of mutations (m) and crossovers (c) are shown on the horizontal axes. The total 
        size of the population is fixed, so the number of random individuals used at each 
        point is 60?-(m+c). This corresponds to the distance from the diagonal.

        [GRAPH]

        The graph above indicates that for a fixed number of evaluations, best results are 
        achieved by selecting parameters that have the majority of individuals in the next 
        generation be generated by crossovers of the most fit schedules in the previous 
        generation. In order to achieve the very highest fitness, a few randoms or mutations 
        should also be incorporated.

        This test was done for only the smallest problem instance, and is infeasible for the 
        larger instances. We chose generation proportion parameters to approximate the optimal 
        values seen here, under the assumption that the larger problems exhibited this sort of 
        preference.

      \paragraph{Size Parameters}
        Blah blah blaj. We investigated the population size and

        [Insert fancy 3D graph here = WIN]

  \subsection{Comparison Between the Different Searches}
    [\ldots]
    \begin{figure}[h!]
  	  \centering
  	  \setlength\fboxsep{0pt}
	  \setlength\fboxrule{0.5pt}
	  \fbox{\includegraphics[width=8.35cm]{HUGE-TYPE2_FullAverageStats}}
      \caption{Search comparison on a large data set}
	\end{figure}
